Efficient Management of Reified Statements in RDF

### 2012-06-07 trunk/paper-iswc-reification/rep.tex
some clarification and a layout improvement

In this section we introduce
	%an extension of the RDF data model~\cite{Klyne04:RDFconcepts} that makes 
	our data model which we call {\RDFplus}. This model is an extension of the RDF data model~\cite{Klyne04:RDFconcepts}. {\RDFplus} extends RDF by making metadata statements a first class citizen in the data model.
% In the following we \todo{...}

@@

{\RDFplus} extends such triples by permitting the embedding of another triple in the subject or object position of a given triple. We shall interpret the embedding triple as a statement about the embedded triple. An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
	%Therefore, the model should allow for nesting.
%
	%As a basis for formalizing
	To formalize
such kind of (nested) embedding we
	%introduce
	define
a set $\symAllTriplesInfinite := (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
%
	As a basis for ruling
	%To rule
out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
	is an arbitrary
	%may be any
natural number): A tuple $(s,p,o) \in \symAllTriplesInfinite$ is $k$-nested if either 1.)~$k=0$ and
	%$(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$
	$(s,p,o)$ is an RDF triple
or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTriplesInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested. Using $k$-nestedness we now define our extended notion of triples%
	.
	%:

>>>>

This section introduces our data model which we call \emph{\RDFplus}. {\RDFplus} extends the RDF data model~\cite{Klyne04:RDFconcepts} by making metadata statements a first class citizen in the data model.
% In the following we \todo{...}

@@

{\RDFplus} extends such triples by permitting the embedding of a given triple in
	%the subject 
	the~subject %%% Layout Adjustment
or object position of another triple. We shall interpret the embedding triple
	%as a statement
	as~a~statement %%% Layout Adjustment
about the embedded triple. An embedded triple may itself be a statement about a triple and, thus, may also contain embedded triples; and so forth.
	%Therefore, the model should allow for nesting.
%
	%As a basis for formalizing
	To formalize
such kind of (nested) embedding we
	%introduce
	define
a set $\symAllTriplesInfinite := (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllTriplesInfinite \cup \symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$.
%
	As a basis for ruling
	%To rule
out infinitely deep nesting we introduce the notion of \emph{$k$-nestedness} (where $k$
	is an arbitrary
	%may be any
natural number): A tuple $(s,p,o) \in \symAllTriplesInfinite$ is $k$-nested if either 1.)~$k=0$ and
	%$(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$
	$(s,p,o)$ is an RDF triple
or 2.)~$k>0$ and for all $x \in \bigl( \lbrace s,o \rbrace \cap \symAllTriplesInfinite \bigr)$ holds $x$ is $(k\!-\!1$)-nested. Using $k$-nestedness we now define our extended notion of triples%
	.
	%:
